\Title

### 2015-10-04 moho-inversion.tex
Tweaks to initial methods section
Moved ETODO and CRUST correction references to real data application
section

\noindent in which $g(P)$ is the measured gravity at an observation point $P$
and $\gamma(P)$ is the gravity of the Normal Earth (the Normal Gravity)
calculated on point $P$.

We assume that the crust of our Normal Earth has a standard density of
$\rho_{crust} = 2670\ kg.m^{-3}$ and a depth to the Moho of $z_{ref}$.
The disturbance contains only the gravitational effects of density
distributions that are anomalous with respect to the Normal Earth.
This includes all masses above the surface of the ellipsoid (the topography),
the mass deficiency of the oceans,
the mass deficiency of sedimentary basins,
crustal sources (e.g., igneous intrusions, lateral density changes, etc),
heterogeneities below the upper mantle,
and
the mass excesses and deficiencies caused by differences between the real Moho
topography and the reference Moho ($z_{ref}$).
The latter is what we are interested in.
In order to invert for the Moho topography, all effects must either be removed
or assumed negligible.
The gravitational effects of topography and sedimentary basins is
removed using the models
ETOPO1\footnote{\url{http://dx.doi.org/10.7289/V5C8276M}}
\citep{amante_c._and_b._w._eakins_etopo1_2009}
and CRUST1.0\footnote{\url{http://igppweb.ucsd.edu/~gabi/rem.html}}
\citep{laske_update_2013}.
Lateral variations in density along the Moho cannot be properly accounted for
in regions where information coverage is sparse and readily accessible models
are not available, like in the South American and African continents.

@@

\noindent in which $d_i$ is the $i$th element of the $N$-dimensional predicted
data vector $\mbf{d}$, $\mbf{p}$ is the $M$-dimensional parameter vector
containing the Moho depths ($z_k$),
and $f_i$ is the $i$th non-linear function that maps the parameters onto the
data.

@@

\begin{equation}
    \mbf{H}(\mbf{p}^k)\mbf{\Delta p} = -\mbf{\nabla}\Gamma(\mbf{p}^k),
\end{equation}

\noindent in which
$\mbf{\nabla}\Gamma$ is the gradient vector and
$\mbf{H}$ is the Hessian matrix of $\Gamma$.
The gradient is given by

\begin{equation}
    \mbf{\nabla}\Gamma(\mbf{p}^k) =
    -2\mbf{A}^T[\mbf{d}^o - \mbf{d}] +
    2\mu\mbf{R}^T\mbf{R}\mbf{p}^k,
    \label{eq:gradient}
\end{equation}

@@

\begin{equation}
    A_{ij} = \dfrac{\partial f_i}{\partial p_j}(\mbf{p^k}).
\end{equation}

\noindent
In practice, the derivative above is often calculated through a first-order
finite-difference approximation.

The first term of \eq{gradient} is the gradient of the data-misfit
function $\phi$ and the second term is the gradient of the regularizing
function $\theta$.

@@

\begin{equation}
    \mbf{H}(\mbf{p}^k) = 2\mbf{A}^T\mbf{A} +
    2\mu\mbf{R}^T\mbf{R}.
    \label{eq:hessian}
\end{equation}

@@

\begin{equation}
    \mbf{\Delta p} = -\mbf{\nabla}\Gamma(\mbf{p}^k).
\end{equation}

@@

Both methods require the computationally expensive evaluation of the Jacobian
matrix $\mbf{A}$.
\todo{Talk a bit about why this is slow and difficult}

@@

\subsection{Satellite gravity data}

Explain where data came from and what was done to  it.

@@

@@

>>>>

\noindent in which $g(P)$ is the measured gravity at an observation point $P$
and $\gamma(P)$ is the gravity of the Normal Earth
calculated at point $P$.

We assume that the crust of our Normal Earth has a standard density of
$\rho_{crust} = 2670\ kg.m^{-3}$ and a depth to the Moho of $z_{ref}$.
The disturbance contains only the gravitational effects of density
distributions that are anomalous with respect to the Normal Earth.
This includes all masses above the surface of the ellipsoid (the topography),
the mass deficiency of the oceans,
the mass deficiency of sedimentary basins,
crustal sources (e.g., igneous intrusions, lateral density changes, etc),
heterogeneities below the upper mantle,
and
the effect of the difference between the real Moho
topography and the reference Moho ($z_{ref}$).
In order to invert for the Moho topography, all effects must either be removed
or assumed negligible.

@@

\noindent in which $d_i$ is the $i$th element of the $N$-dimensional predicted
data vector $\mbf{d}$, $\mbf{p}$ is the $M$-dimensional parameter vector
containing the Moho depths ($z_k$),
and $f_i$ is the $i$th non-linear function that maps the parameters onto the
data.
\todo{Say something about tesseroid forward modeling and cite paper.}

@@

\begin{equation}
    \mbf{H}^k\mbf{\Delta p} = -\mbf{\nabla}\Gamma^k,
\end{equation}

\noindent in which
$\mbf{\nabla}\Gamma^k$ is the gradient vector and
$\mbf{H}^k$ is the Hessian matrix of $\Gamma$.

The gradient is given by

\begin{equation}
    \mbf{\nabla}\Gamma^k =
    -2\mbf{A}^T[\mbf{d}^o - \mbf{d}(\mbf{p}^k)] +
    2\mu\mbf{R}^T\mbf{R}\mbf{p}^k,
    \label{eq:gradient}
\end{equation}

@@

\begin{equation}
    A_{ij} = \dfrac{\partial f_i}{\partial p_j}(\mbf{p^k}).
    \label{eq:jacobian}
\end{equation}

\noindent
The first term of \eq{gradient} is the gradient of the data-misfit
function $\phi$ and the second term is the gradient of the regularizing
function $\theta$.

@@

\begin{equation}
    \mbf{H}^k = 2\mbf{A}^T\mbf{A} +
    2\mu\mbf{R}^T\mbf{R}.
    \label{eq:hessian}
\end{equation}

@@

\begin{equation}
    \mbf{\Delta p} = -\mbf{\nabla}\Gamma^k.
\end{equation}

@@

Both methods require the computationally expensive evaluation of the Jacobian
matrix $\mbf{A}$.
In practice, the derivative in \eq{jacobian} is often calculated through a
first-order finite-difference approximation.
Thus, evaluating $\mbf{A}$ requires $2\times M \times N$ forward modeling
operations for each iteration of the gradient descent algorithm.
When using tesseroids, forward modeling requires several trigonometric function
evaluations as well as adaptive discretization.
\todo{Cite forward modeling paper}
Both factor contribute significantly to the total computation time.

@@

@@

\subsection{Gravity data}

The gravitational effect of the topography
is removed using the
ETOPO1\footnote{\url{http://dx.doi.org/10.7289/V5C8276M}}
digital terrain model
\citep{amante_c._and_b._w._eakins_etopo1_2009}.
The effect of sedimentary basins is removed using the
CRUST1.0\footnote{\url{http://igppweb.ucsd.edu/~gabi/rem.html}} model
by
\citet{laske_update_2013}.
Lateral variations in density along the Moho cannot be properly accounted for
in regions where information coverage is sparse and readily accessible models
are not available, like in the South American and African continents.
For the purposes of this study, we will assume that all other crustal sources
and lateral variations in density are negligible.

@@

\subsection{Inversion results}
